\documentclass[12pt]{article} % Default font size is 12pt, it can be changed here

\usepackage{graphicx} % Required for including pictures
%\usepackage{float} % Allows putting an [H] in \begin{figure} to specify the exact location of the figure
%\usepackage{floatrow}
\usepackage{wrapfig} % Allows in-line images such as the example fish picture
\usepackage[margin=1in, paperwidth=8.5in, paperheight=11in]{geometry}
\usepackage{fixltx2e}

\setcounter{tocdepth}{5} %to make it appears in TOC
\setcounter{secnumdepth}{5} %to make it numbered

\linespread{1.2} % Line spacing

\setlength\parindent{0pt} % Uncomment to remove all indentation from paragraphs

\graphicspath{{./Pictures/}} % Specifies the directory where pictures are stored

\date{}

\begin{document}

\title{Clich\'{e} Zombie Game}
\maketitle

\section{Introduction}

It's finally happened - the zombie apocalypse.  Why didn't you listen to your poor grandma when she told you to be prepared for this day?  Now you are stranded in a zombie wasteland with your "friends" - let's be honest, they don't like you and you don't like them, but if you all work together, you all may make it out alive.  You've heard of a paradise that is zombie free - Canada.  But there's no way to safely travel such a long distance through the zombie infested fields without a vehicle, and all the working ones were quickly snatched up.  If you could only build a car before the zombies devourer you...

\section{Pieces}

\begin{itemize}
	\item 1x Resource Card Board
	\item 1x Deck of Resource Cards
	\item 1x Green Human 6-sided Die
	\item 8x Orange Zombie 6-sided Dice
	\item 8x Bite Tokens
	\item 8x Zombie Cards
	\item 1x Human-Start Card
	\item 7x Zombie Tokens
	\item 1x Human Token
\end{itemize}

\section{Resource Cards}
There are 5 different cards in the resource deck - scrap metal (blank cards), engines, tires, medkits and shotguns.  

\subsection{Scrap Metal}
Scrap Metal serves two purposes - first, as one of the components for the car; and second, as currency for trading.

\subsection{Engines and Tires}
Engines and tires serve only as components for building the car.  Engines can be exchanged for six scrap metal and tires for four.

\subsection{Medkits}
Medkits can be used between rounds to remove one bite token from any player.  A medkit is placed in the trash pile after being used.  Medkits can be exchanged for three scrap metal.

\subsection{Shotguns}
Shotguns are used during the rounds to immediately kill a zombie that is either directly in front of or directly behind the human.  To use the shotgun, it must be placed face-up in front of the player before the start of the round.  Keeping it in hand makes it unavailable.  Shotguns can be exchanged for three scrap metal.

\section{Starting the Game}

\subsection{}
At the beginning of the game, one player will be a zombie.  That number can grow over the course of the game.  To decide to initial zombie, all players roll for the highest number.  The player with the highest die roll chooses which player will be the zombie.  He may choose himself.  Give the chosen player a zombie card.  Place the human-start card in front of one of the human players.

\subsection{}
Place the board in the center of the table within reach of all players.  Shuffle the deck of resource cards and place it face-down on the deck square.  Each zombie draws three resource cards.  Players keep their hands hidden from each other.  Place the human token on the H space and a zombie token on the Z\textsubscript{1} space.

\section{Rounds}
Rounds are played until either a victory condition is met, or all players become zombies.  Each round has the following phases: Setup, Gathering, Trading and Clean Up.

\subsection{Setup}

During the setup phase place the human die in front of the player with the human-start card, and place zombie dice in front of all players who are zombies.  Place the human token on the H space and place zombie tokens on spaces Z\textsubscript{1}-Z\textsubscript{7}, going up to as many zombies as there currently are.  For example, with one zombie, it would go on Z\textsubscript{1}; with 2, the would go on Z\textsubscript{1} and Z\textsubscript{2}, and so on.  Any player who has a shotgun in her hand and wishes it to be available for the upcoming gathering phase should place it in front of her during this phase.

\subsection{Gathering}
The gathering phase is when the party ventures out into the field to attempt to find resources.  But, of courses, there are zombies to contend with.  

\subsubsection{}
All players with a die roll it as quickly as they can to try and have it land on a '1'.  When a human player rolls a '1', he moves the human token one space clockwise, and passes the die around the table clockwise to the next human player and that player does the same - rolling until a '1'.  If there are no other human players, he just keeps rolling.  When a zombie player rolls a '1', he moves his zombie token one space clockwise, and then continues rolling.  He does not pass his die.  Players keep rolling the dice and passing until one of the following situations.

\paragraph{}
If the human token catches up to a zombie token, the zombie is "killed" and the zombie token is removed from play.  If there are no other zombie tokens left in play, the gathering phase is over with the humans successful and all human players draw two resource cards from the deck.

\paragraph{}
If a zombie token catches up to the human token, the player who currently has the human die gets "bitten" and the round is over.  If that player has no bite tokens, he gets one.  If he already has a bite token, then he becomes a zombie.  He returns his bite token, places all of his resource cards in the trash pile, and gets a zombie card.  All humans besides the one who was bitten draw one resource card. \newline 

\paragraph{}
If a player has a shotgun in front of him and he currently has the human die, he may use the shotgun.  The shotgun can be used to instantly kill a zombie token that is directly in front of or directly behind the human token.  If that player has the human die when the human token is caught by the zombie token, the shotgun is automatically used to kill the zombie and save the human from being bitten.  After using the shotgun, the card is put into the trash pile.  If the shotgun killed the last zombie die, the gathering phase ends as usual, if not, the round continues.

\subsection{Trading}

\subsubsection{}
The first step of the trading phase is to deal cards from the deck into the five trading spaces on the board.  The first card going into the space marked '1' and then working right until '8'.  If all the cards turned up are scrap, then the five scrap are put into the trash and five new cards are dealt.  Keep dealing until at least one non-scrap card is turned up.

\subsubsection{}
The order of trading is determined by the results of the gathering phase.  If the humans caught the zombie, the first player to trade is the player who was the last to roll the die and trading proceeds counter-clockwise.  If during the gathering phase the zombies caught the human then the first player to trade is the player to the right of the human who was caught and trading goes counter-clockwise.  

\subsubsection{}
During each player's turn to trade, if he is a human, he may either trade for one of the face-up cards or exchange one of this non-scrap cards for scrap but not both.  To trade, the player must pay X scrap from his hand, where X is the number indicated on the square that the card is on.  He puts the scrap into the trash and the new card into his hand. To exchange one of the resources he currently has for scrap, he puts the resource card into the trash and takes the designated number of scrap out of the trash - 3 for medkits and shotguns, 4 for tires and 6 for engines.  If the trash does not have enough scrap he may take as much as is there, or cancel the exchange.  He may opt to do neither of these and just pass to the next player.  \newline

If the player is a zombie, he may place any one of the cards into the trash and replace it with a new card from the deck.  After all players have had a turn, the remaining face-up cards are put into the trash.

\subsubsection{}
After that, human players may freely trade amongst themselves, medkits may be used, and vehicles may be built.

\subsubsection{}
If at any time the deck runs out of cards, shuffle the trash pile and place it onto the deck location.

\subsection{Clean Up}
Once trading is finished, the round will end.  The human-start card is passed clockwise to the next human player.

\section{Victory}
There are two victory conditions:

\subsection{Building a Car}
If during the trading phase, all the human players together have 1 engine, 4 tires and 30 scrap, they can build a car and all the remaining humans win.

\subsection{Building a Motorcycle}
If during the trading phase a single player has 1 engine, 2 tires and 10 scrap, she can build a motorcycle to escape on her own.  That player is the only winner.

\end{document}